Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-03-31 paper/notes.tex
Tuesday's later afternoon notes

The initial model is derived from the one in the Barrels
paper~\cite{james_modelling_2020} which is found
in \code{sim/rd\_barrel.h}. The specialization of \code{RD\_Barrel} can be
found in \code{sim/rd\_rettec.h}, with main code file \code{rettec.cpp}. Here,
instead of providing interaction parameters ($\gamma_{i,j}$) in a
configuration file, I use only the parameter $N$, which in this context is the
number of neurons originating in the retina. I automatically arrange these $N$
retinal neurons in a radially symmetric pattern. I then obtain the $gamma$
parameters from the neuron locations within the pattern.

@@

@@

The operation of the model without modifiction and with zero or low noise.

>>>>

The initial model is derived from the one in the Barrels
paper~\cite{james_modelling_2020} which is found
in \code{sim/rd\_barrel.h}. The specialization of \code{RD\_Barrel} (and a
sister class, \code{RetArrange}) can be found in \code{sim/rd\_rettec.h}, with
main code file \code{rettec.cpp}. Here, instead of providing interaction
parameters ($\gamma_{i,j}$) in a configuration file, I use only the parameter
$N$, which in this context is the number of neurons originating in the
retina. I automatically arrange these $N$ retinal neurons in a radially
symmetric pattern (See \code{RetArrange}). I then obtain the $\gamma$
parameters from the neuron locations within the pattern.

@@

\subsection{Non-competition based stopping mechanism}

Starting from the branching equation again (but dropping the competition term,
$\chi_i$):

\begin{equation} \label{eq:da_again}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right) - \frac{\partial c_i}{\partial t},
\end{equation}

The spatial part of the system can be halted if $D\rightarrow
0, \gamma_{i,j}\rightarrow 0$ as
$f(\gamma_{i,1},\gamma_{i,2},...,\gamma{i,M})\rightarrow 1$. That is, if, for
a particular axon, $i$, a sampling of $\rho_j$ is close to $f(\gamma_{i,j})$
for each $j$, then $D$ is reduced to zero, and likewise, the second term also
reduces to zero. $f()$ is probably $1-$ a (possibly noisy) normalized Gaussian
function, or a capped Gaussian (with height capped by a sigmoid?), with mean
$(\gamma_{i,1},\gamma_{i,2})$ and a width based on the differences between
$\gamma_{i\pm 1,j}$. Something like:

\begin{equation} \label{eq:da_stopping}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M=2} \gamma_{i,j}\nabla \rho_j(\mb{x})\right)\;f(\gamma_{i,1},\gamma_{i,2},\mb{x}) - \frac{\partial c_i}{\partial t},
\end{equation}

$f$ could be thought of as a functional:
$f_i[\gamma_{i,1},\gamma_{i,2}](\mb{x})$ (if that's the right way to write
it...).

Let's try to write f out. See gaussians.m initially.

@@

The operation of the model without modification and with zero or low noise.
